My Statistics 3494W Proposal

### 2022-10-05 Proposal/Proposal.tex
commit #conclusion

\bibliographystyle{chicago}
\bibliography{citations.bib}
\end{document}

>>>>

\section*{Conclusion}
Overall, my research can provide excellent insight into forecasting call center data. I can help finanical firms with ways to deal with spikes in 
calls and how to be efficient during the least amount of activity throughout the day. I will set a new standard on how agents should be operating to set
a baseline on performance. With the amount of data at my hands, there is also an opportunity for others to collaborate and extend this analysis after this semester.
\bibliographystyle{chicago}
\bibliography{citations.bib}
\end{document}
